### 2012-06-27 inst/examples/cautious.Rmd
caution curves

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

 * Author [Carl Boettiger](http://carlboettiger.info), <cboettig@gmail.com>
 * License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)
 * Description:  Implements a numerical version of the SDP described in `r knitcitations::citet("10.1016/0095-0696(79)90014-7")`, in which the dynamics are slowly moving towards a tipping point.

@@

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=16)
````

@@

``` {r policyfn_plot, dependson="find_dp_opt"}
require(reshape2)
policy <- melt(as.data.frame(cbind(stock=x_grid, sapply(opts, function(x) x$D[,1])), id="stock")
ggplot(policy) + geom_lines(aes(stock, value, color=variable))
````

>>>>

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
````

@@

 * Author [Carl Boettiger](http://carlboettiger.info), <cboettig@gmail.com>
 * License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)

@@

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=2)
````

@@

``` {r policyfn_plot, dependson="find_dp_opt"}
require(reshape2)
dat <- sapply(opts, function(x) x$D[,1])
dat <- as.data.frame(cbind(stock=x_grid, dat))
names(dat) <- c("stock", as.character(round(P,2)))
policy <- melt(dat, id="stock")
ggplot(policy) + geom_line(aes(stock,x_grid - x_grid[value], color=variable)) + ylab("escapement")
````

``` {r valuefn_plot, dependson="find_dp_opt"}
dat <- sapply(opts, function(x) x$V)
dat <- as.data.frame(cbind(stock=x_grid, dat))
names(dat) <- c("stock", as.character(round(P,2)))
policy <- melt(dat, id="stock")
ggplot(policy) + geom_line(aes(stock, value, color=variable)) + ylab("Net present value")

x0_i <- which.min(abs(x_grid-K))
values <- sapply(opts, function(x) x$V[x0_i])
names(values) <- as.character(round(P,2))
values
````
